discussion

### 2018-01-18 man/ms_1_material_methods.Rmd
update text

$$\mathrm{EVI_{sa,\mathit{i}}}= \frac{\mathrm{EVI_{mean,\mathit{i}}-EVI_{mean,ref}}}{\sigma_{\mathrm{ref}}}$$
where $\mathrm{EVI_{sa,\mathit{i}}}$ is the EVI standardized anomaly for the year $i$;  $\mathrm{EVI_{mean,\mathit{i}}}$ the annual mean value of EVI for the year $i$; $\mathrm{EVI_{mean,ref}}$ the average of the annual EVI values for the period of reference (all except $i$ year), and $\sigma_{\mathrm{ref}}$ the standard deviation for the reference period. Each pixel was categorized according the EVI standardized anomalies as "greening" (EVI standardized anomalies greater than + 1), "browning" (EVI standardized anomalies less than - 1) or "no changes" (EVI standardized anomalies between − 1 and  + 1) (incluir cita). 
## Field sampling and dendrochronological methods

>>>>

$$\mathrm{EVI_{sa,\mathit{i}}}= \frac{\mathrm{EVI_{mean,\mathit{i}}-EVI_{mean,ref}}}{\sigma_{\mathrm{ref}}}$$
where $\mathrm{EVI_{sa,\mathit{i}}}$ is the EVI standardized anomaly for the year $i$;  $\mathrm{EVI_{mean,\mathit{i}}}$ the annual mean value of EVI for the year $i$; $\mathrm{EVI_{mean,ref}}$ the average of the annual EVI values for the period of reference (all except $i$ year), and $\sigma_{\mathrm{ref}}$ the standard deviation for the reference period. Each pixel was categorized according the EVI standardized anomalies as "greening" (EVI standardized anomalies greater than + 1), "browning" (EVI standardized anomalies less than - 1) or "no changes" (EVI standardized anomalies between − 1 and  + 1) [@Samanta2010; @Samanta2012].

## Field sampling and dendrochronological methods

### 2018-01-18 man/ms_2_results.Rmd
update text

```{r}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
```

@@

Vegetation greenness of *Quercus pyrenaica* forests were lower during the 2005 and 2012 year than the greenness observed for the reference period (Fig. R1 Profile EVI). The lowest values for EVI standardized anomalies were recorded in 2005 being singnificantly lower (-2.285 ± 0.029) than 2012 (-0.418 ± 0.029) (LSMEANS, t.ratio = -45.358; p_value < 0.0001), particularly for northern populations (Fig. R2 y R3).

Esta disminución para 2005 sin embargo fue heterogénea (ver plot de trajectorias)

Durante 2005 la mayoría de los pixeles mostraron browning (99.36 % y 79.37 % para las poblaciones del norte y del sur respectivamente), sin embargo en 2012 la mayoría de los pixeles se clasificaron como no changes en las poblaciones del norte (89.60 %) y en las del sur (70.07 %) (Tabla supplementaria??)

@@

```{r echo=FALSE, results='asis', eval=show_text}
cat("
> Cuando exploramos las anomalías (brutas, estandarizadas y normalizadas) observamos valores muy negativos para el año 2005. Sin embargo vemos valores menos negativos para 2005. Tukey posthoc testing (lsmeans package CITAR) was conducted for pairwise comparisons among the slopes and the disturbance years

@@

> * En 2005 y en 2012 las anomalías fueron negativas.
> Reduction in annual EVI mean was considerably higher in northern populations than in southern ones during the 2005 drought.")
```

@@

Si analizamos el plot de trajectorias (evi medio anual), vemos como en 2005 y 2012 se observó un browning para los valores medios de EVI. En ambos casos, se observó un patrón homogéneo de browing, aunque en 2012 el browning fue mucho menor.

>>>>

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
```

@@

Trends analysis showed that 78.9 % of the pixels of *Q. pyrenaica* forests experienced an EVI positive trend for the 2000-2016 period, of which 31.67 % were significant trends. The strongest trends were observed in southwestern populations (Figura S2). Vegetation greenness of *Quercus pyrenaica* forests were lower during the 2005 and 2012 year than the greenness observed for the reference period (Figure 2a). The lowest values for EVI standardized anomalies were recorded in 2005 being singnificantly lower (-2.285 ± 0.029) than 2012 (-0.418 ± 0.029) (LSMEANS, t.ratio = -45.358; p_value < 0.0001), particularly for northern populations (Figure 2b). Reduction in annual EVI mean was considerably higher in northern populations than in southern ones during the 2005 drought (Figure 2b).

According to the standardized anomalies, *Q. pyrenaica* forests suffered a browning during 2005 drought event (99.36 % and 79.37 % of the pixels for northern and southern populations respectively), however no changes were observed for the 2012 drought (Figure S3).

```{r echo=FALSE, results='asis', eval=show_text}
cat("
* Disminución del EVI --> Espacialización ver plots de trajectorias
* Por ejemplo la disminución para 2005 fue heterogénea (

* Durante 2005 la mayoría de los pixeles mostraron browning (99.36 % y 79.37 % para las poblaciones del norte y del sur respectivamente), sin embargo en 2012 la mayoría de los pixeles se clasificaron como no changes en las poblaciones del norte (89.60 %) y en las del sur (70.07 %) (Tabla supplementaria??)

@@

> Cuando exploramos las anomalías (brutas, estandarizadas y normalizadas) observamos valores muy negativos para el año 2005. Sin embargo vemos valores menos negativos para 2005. Tukey posthoc testing (lsmeans package CITAR) was conducted for pairwise comparisons among the slopes and the disturbance years

@@

> * En 2005 y en 2012 las anomalías fueron negativas.
> Reduction in annual EVI mean was considerably higher in northern populations than in southern ones during the 2005 drought.

@@

Si analizamos el plot de trajectorias (evi medio anual), vemos como en 2005 y 2012 se observó un browning para los valores medios de EVI. En ambos casos, se observó un patrón homogéneo de browing, aunque en 2012 el browning fue mucho menor. 
")
```

### 2018-01-18 man/ms_3_discussion.Rmd
update ms
update text

---
title: "discussion"
author: "AJ Perez-Luque (@ajpelu); G. Gea-Izquierdo"
date: "2017"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../references.bib
csl: ../ecology.csl
---

@@

>>>>

---
title: "discussion"
author: "AJ Perez-Luque (@ajpelu); G. Gea-Izquierdo"
date: "2017"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

@@

## Greenness

* Aproximadamete el x% de los robledales mostraron un incremento en los valores de productividad (greenees) ... (relacionar con tendencias EVI y ontologias).
* tendencias ontologias

* Si analizamos el plot de trajectorias (evi medio anual), vemos como en 2005 y 2012 se observó un browning para los valores medios de EVI. En ambos casos, se observó un patrón homogéneo de browing, aunque en 2012 el browning fue mucho menor.
